LSTM for Sentiment Analysis on Twitter

### 2015-12-20 paper/paper.tex
add some refs
add some figs
fill in some results, add a fig

\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\newcommand\BibTeX{B{\sc ib}\TeX}

@@

@@

\section{Experiments}
See Table ~\ref{sample-table} for awesome results

\begin{table}[h]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

This is a figure:

\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\newcommand\BibTeX{B{\sc ib}\TeX}

@@

Dynamic convolutional neural net for sentences \cite{kalchbrenner2014convolutional}

sentiment specific word embeddings \cite{tang2014learning}

character-lvl CNN for text classification \cite{zhang2015character}

@@

\section{Experiments}

\subsection{Datasets}

\subsection{Results}

\begin{table}[h!]
\centering
\caption{Accuracy across LSTMs}
\label{char-models}
\begin{tabular}{|l|ll|}
\hline
              & 1.6M           & semeval \\
\hline
ascii/rnd/50  & \textbf{83.84} & 82.08   \\
ascii/rnd/200 & 82.45          & 83.53   \\
ascii/eye/50  & 77.44          &         \\
utf8          & 81.34          & 82.34   \\
word/rnd      & 81.85          & 78.07   \\
word/sswe     & 83.24          & 79.27   \\
\hline
\end{tabular}
\end{table}

\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\includegraphics[width=0.95\textwidth]{figs/cool}
%\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\includegraphics[width=0.95\textwidth]{figs/puppies}
%\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\includegraphics[width=0.95\textwidth]{figs/cool}
%\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\includegraphics[width=0.95\textwidth]{figs/dentist}
%\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Confidence in ``negative'' prediction over time}
\end{figure}
